### 2012-06-21 inst/examples/voi_sethi_parameters.Rmd
updated zero with the cautious optimization fn

``` {r simfn} 
simulatereps <- function(opt, true_g, true_m, true_i){
  z_g <- function() rlnorm(1,  0, true_g) 
  z_m <- function() rlnorm(1,  0, true_m) 
  z_i <- function() rlnorm(1,  0, true_i)

@@

#  list(sims = sims, opt = opt, true_stochasticity = c(true_g, true_m, true_i))
  sims
}
````

@@

``` {r runallsims} 
policyfn <- list(det=det, g=g, m=m, i=i, gm=gm, gi=gi, gmi=gmi)
noise <- list(s0=c(0,0,0), sg=c(lvl, 0, 0), sm=c(0, lvl, 0), si=c(0,0,lvl), sgm=c(lvl, lvl, 0), sgi=c(lvl, 0, lvl), sgmi=c(lvl, lvl, lvl)) 
allcases <- lapply(policyfn, function(policyfn_i){
  lapply(noise, function(noise_i){
    simulatereps(policyfn_i, noise_i[1], noise_i[2], noise_i[3])
  })
})
````

``` {r tidyall}
sims <- unlist(allcases, recursive=FALSE)
dat <- melt(sims, id=names(sims[[1]][[1]]))  
dt <- data.table(dat)
setnames(dt, c("L2", "L1"), c("reps", "uncertainty")) # names are nice
````

>>>>

``` {r simfn} 
simulatereps <- function(opt, true_g, true_m, true_i){

  z_g <- function() 1+(2*runif(1, 0,  1)-1) * true_g
  z_m <- function() 1+(2*runif(1, 0,  1)-1) * true_m
  z_i <- function() 1+(2*runif(1, 0,  1)-1) * true_i

@@

  sims
}
````

@@

``` {r runallsims, dependson="simfn"} 
policyfn <- list(det=det, g=g, m=m, i=i, gm=gm, gi=gi, gmi=gmi)
noise <- list(s0=c(0,0,0), sg=c(lvl, 0, 0), sm=c(0, lvl, 0), si=c(0,0,lvl), sgm=c(lvl, lvl, 0), sgi=c(lvl, 0, lvl), sgmi=c(lvl, lvl, lvl)) 
allcases <- lapply(policyfn, function(policyfn_i){
  lapply(noise, function(noise_i){
    simulatereps(policyfn_i, noise_i[1], noise_i[2], noise_i[3])
  })
})
````

``` {r tidyall, dependson="runallsims"}
sims <- unlist(allcases, recursive=FALSE)
dat <- melt(sims, id=names(sims[[1]][[1]]))  
dt <- data.table(dat)
setnames(dt, c("L2", "L1"), c("reps", "uncertainty")) # names are nice
````
